Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-18 latex/comp_or.tex
Continue tests in Calypso

\subsection{Instances generation}
\label{items}

@@

@@

The testing experiments are performed on a 64-bit, 16GiB, 3.2GHz, 8-core processor, 2 threads per core, AMD FX-8320E, with {\it Linux Ubuntu 22.04} as the operational system and {\it Python 3.10.4}\/ as the programming language.

The final experiments are performed on a 64-bit, 128GiB, 3.6GHz, 48-core processor, 2 threads per core, Intel Xeon, with {\it Linux CentOS 8} as the operational system and {\it Python 3.8.2}\/ as the programming language.

@@

\begin{algorithm}[H]
	\caption{$getBestNPP(procs, scores, runtimes)$}  \label{alg:bestnum}
	\begin{algorithmic}[1]
		\State $maxS   \gets max(scores)$
		\State $minS   \gets min(scores)$
		\State $maxR \gets max(runtimes)$
		\State $minR \gets min(runtimes)$

@@

		\For{$i$ in $procs$}
			\State $y = ( maxS - scores[i] )\ /\ (maxS   - minS  )$
			\State $x = ( runtimes[i] - minR )\ /\ (maxR - minR)$
			\State $h = \sqrt{x^2 + y^2}$, distance from {\it Utopia}
			\If{$minD$ > $h$}
				\State $minD \gets h$
				\State $bestNPP \gets procs[i]$
			\EndIf

@@

\multirow{3}{*}{\it {mpShims}} &$1.2$& 6       & 2     & 0     & 0     & 0     & 0    \\ 
                               &$1.5$& 4       & 4     & 0     & 0     & 0     & 0    \\
                               &$2.0$& 0       & 0     & 0     & 0     & 0     & 0    \\
\midrule[.1pt]

\multirow{3}{*}{\it {mpACO}}   &$1.2$& 4       & 2     & 0     & 0     & 0     & 0    \\ 
                               &$1.5$& 6       & 1     & 0     & 0     & 0     & 0    \\ 
                               &$2.0$& 0       & 0     & 0     & 0     & 0     & 0    \\                               
\bottomrule		
\end{tabular}

@@

Table \ref{tab:numProcs} presents the best numbers of parallel processes for each method, scenario, and volume surplus.

>>>>

\subsection{Items generation}
\label{items}

@@

We test our methods with 126 different instances because we have six operational scenarios with seven randomly generated item sets for three volume surpluses (1.2, 1.5, and 2.0 times aircraft volume capacities).

@@

%The testing experiments are performed on a 64-bit, 16GiB, 3.2GHz, 8-core processor, 2 threads per core, AMD FX-8320E, with {\it Linux Ubuntu 22.04} as the operational system and {\it Python 3.10.4}\/ as the programming language.

The final experiments are performed on a 64-bit, 128GiB, 3.6GHz, 48-core processor, 2 threads per core, Intel Xeon, with {\it Linux CentOS 8} as the operational system and {\it Python 3.8.2} as the programming language.

@@

\begin{algorithm}[H]
	\caption{$getBestNPP(scores, runtimes, procs)$}  \label{alg:bestnum}
	\begin{algorithmic}[1]
		\State $maxS   \gets max(scores)$
		\State $minS   \gets min(scores)$
		\State $maxR \gets max(runtimes)$
		\State $minR \gets min(runtimes)$

@@

		\For{$i \in |scores|$}
			\State $y = ( maxS - scores[i] )\ /\ (maxS   - minS  )$, the Y axis leg of Figure \ref{fig:scenario1data20}
			\State $x = ( runtimes[i] - minR )\ /\ (maxR - minR)$. the X axis leg
			\State $h = \sqrt{x^2 + y^2}$, the hypotenuse, distance from {\it Utopia}
			\If{$minD$ > $h$}
				\State $minD \gets h$
				\State $bestNPP \gets procs[i]$
			\EndIf

@@

\multirow{3}{*}{\it {mpShims}} &$1.2$& 6       & 4     & 4     & 4     & 2     & 2    \\ 
                               &$1.5$& 4       & 4     & 4     & 4     & 4     & 4    \\
                               &$2.0$& 4       & 4     & 4     & 2     & 2     & 4    \\
\midrule[.1pt]

\multirow{3}{*}{\it {mpACO}}   &$1.2$& 10      & 8     & 10    & 6     & 10     & 10    \\ 
                               &$1.5$& 6       & 1     & 0     & 0     & 0     & 0    \\ 
                               &$2.0$& 0       & 0     & 0     & 0     & 0     & 0    \\                               
\bottomrule		
\end{tabular}

@@

Table \ref{tab:numProcs} presents the best numbers of parallel processes for each method, scenario, and volume surplus. As all numbers are less than or equal to 8, any hand-held computer with 8 cores can yield efficient solutions.
